Sequential and parallel algorithms for multidimensional multiextremal optimization based on the nested scheme of dimensionality reduction

### 2017-09-01 2017/ParOptBook/Chapter5.tex
Added items remotely
D:\Common\Barkalov\Публикации\2016 ParOptBook Eng\LaTeX\Chapter4.tex
D:\Common\Barkalov\Публикации\2016 ParOptBook Eng\LaTeX\Chapter5.tex
D:\Common\Barkalov\Публикации\2016 ParOptBook Eng\LaTeX\Chapter6.tex
D:\Common\Barkalov\Публикации\2016 ParOptBook Eng\LaTeX\Chapter7.tex
D:\Common\Barkalov\Публикации\2016 ParOptBook Eng\LaTeX\Chapter8.tex
D:\Common\Barkalov\Публикации\2016 ParOptBook Eng\LaTeX\dedic.tex
D:\Common\Barkalov\Публикации\2016 ParOptBook Eng\LaTeX\editor.tex
D:\Common\Barkalov\Публикации\2016 ParOptBook Eng\LaTeX\foreword.tex
D:\Common\Barkalov\Публикации\20

\title{Parallel computations for the multidimensional multiextremal optimization problems with the dimensionality reduction using Peano curves}
% Use \titlerunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\author{Name of First Author and Name of Second Author}
% Use \authorrunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\institute{Name of First Author \at Name, Address of Institute, \email{name@email.address}
\and Name of Second Author \at Name, Address of Institute \email{name@email.address}}
%
% Use the package "url.sty" to avoid
% problems with special characters
% used in your e-mail or web address
%
\maketitle

@@

>>>>

\title{Sequential and parallel algorithms for multidimensional multiextremal optimization based on the nested scheme of dimensionality reduction}
% Use \titlerunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\author{Name of First Author and Name of Second Author}
% Use \authorrunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\institute{Name of First Author \at Name, Address of Institute, \email{name@email.address}
\and Name of Second Author \at Name, Address of Institute \email{name@email.address}}
%
% Use the package "url.sty" to avoid
% problems with special characters
% used in your e-mail or web address
%
\maketitle

@@

Instead of simply listing headings of different levels we recommend to let every heading be followed by at least a short passage of text. Further on please use the \LaTeX\ automatism for all your cross-references and citations. And please note that the first line of text that follows a heading is not indented, whereas the first lines of all subsequent paragraphs are.
